Foreground Detection via Deep Variation Transformation

### 2018-12-10 draft.tex
revised to the paragraph 1 of second subsection in IV

\subsection*{Network Work Architecture and Variation Transformation}
As shown in the \reffig{flow_chart},
a end-to-end architecture network is proposed to transform the observations of pixels to a new space which is close to labels.
%
The input of network is the training patches $S(m,n)$ extracted from different pixels
and the output of network is the labeled patches captured from Groundtruth frames.
%
The training procedure is the transformation from the training patches to the labelling patches,
which is shown as follows:
% 
% the architecture of network 
% 
% Correspondingly, the groundtruth patches are obtained in a similar way as the input ones, except the concatenation process, as shown in the \reffig{flow_chart}. 
% Both of them are fed into the network for training to find a end-to-end transformation at each pixel position. 
% However, the size of feature maps will shrink quickly during forward computation. 
% In preprocessing, we borrow the idea from Image Semantic Segmentation \cite{Shelhamer2017fcn}, padding the input patches before the training. 
% After the forward computing, observations in input patches are mapped into a new space where they can be easily classified by thresholding. 
% The transformed pixel patch is defined as:
\begin{equation}
    \begin{split}
        S'(m,n) & = f_{\theta_N} ( f_{\theta_{N - 1}} ( \cdots f_{\theta_1} (Pad(S(m,n))) \cdots  ) )  \\
          & = f_{ \prod_{n=1}^{N}\theta_n   }^n(S(m,n)),
    \end{split}
\end{equation}
where, $S'(m,n)$ is the prediction of the network, and the forward computation at each layer of the network is represented by $f_{\theta_N}$. The symmetric padding process is denoted as $Pad$, where we have lost none of the pixel information to make the output $S'(m,n)$ the same size as the pixel patch $S(m,n)$. 
Another advantage of symmetric padding is that the order information still remains.

>>>>

\subsection*{Network Work Architecture and Variation Transformation}
% 先描述动机
As we mentioned above,
the main purpose of our DPVTL is trying to transform the sequence of pixels' observations 
into another space where the observations are easier classified.
% 分析问题，提出解决的方案，要用数学化的形式
Therefore,
our network entails learning a mapping from the input observations of pixels $x \in \mathcal{X}$ 
to the probability of the corresponding pixel belong to foreground or background.

As shown in the \reffig{flow_chart},
a end-to-end architecture network is proposed to transform the observations of pixels to a new space which is close to labels.
%
The input of network is the training patches $S(m,n)$ extracted from different pixels
and the output of network is the labeled patches captured from Groundtruth frames.
%
The training procedure is the transformation from the training patches to the labelling patches,
which is shown as follows:
% 
% the architecture of network 
% 
% Correspondingly, the groundtruth patches are obtained in a similar way as the input ones, except the concatenation process, as shown in the \reffig{flow_chart}. 
% Both of them are fed into the network for training to find a end-to-end transformation at each pixel position. 
% However, the size of feature maps will shrink quickly during forward computation. 
% In preprocessing, we borrow the idea from Image Semantic Segmentation \cite{Shelhamer2017fcn}, padding the input patches before the training. 
% After the forward computing, observations in input patches are mapped into a new space where they can be easily classified by thresholding. 
% The transformed pixel patch is defined as:
\begin{equation}
    \begin{split}
        S'(m,n) & = f_{\theta_N} ( f_{\theta_{N - 1}} ( \cdots f_{\theta_1} (Pad(S(m,n))) \cdots  ) )  \\
          & = f_{ \prod_{n=1}^{N}\theta_n   }^n(S(m,n)),
    \end{split}
\end{equation}
where, $S'(m,n)$ is the prediction of the network, and the forward computation at each layer of the network is represented by $f_{\theta_N}$. The symmetric padding process is denoted as $Pad$, where we have lost none of the pixel information to make the output $S'(m,n)$ the same size as the pixel patch $S(m,n)$. 
Another advantage of symmetric padding is that the order information still remains.
